### 2017-06-14 manuscript/manuscript.Rmd
Create a table of specific reproducibility challenges addressed by Git

>>>>

<!-- Examples of problems in psychology solved by VCS somewhere here. -->

\noindent
\fbox{\begin{minipage}{\textwidth}
  \begin{itemize}
    \item Problem: Researchers usually want to try different ways of visualizing and modeling their data, and sometimes it is difficult to keep track of all the different versions.
      \begin{itemize}
        \item Solution: VCS allows researchers to save each version of the analysis into a history from where it can be easily recalled. This approach also eschews the need for creating multiple copies of the same analysis files with small tweaks, as illustrated \href{http://phdcomics.com/comics/archive.php?comicid=1531}{here}.
      \end{itemize}
  \end{itemize}
  \begin{itemize}
    \item Problem:
      \begin{itemize}
        \item Solution:
      \end{itemize}
  \end{itemize}
\end{minipage}}
